---
title: "hw7"
format: html
editor: visual
---

## 

4.  a\)

```{r}
treaty <- read.csv("treaty.csv")

covs <- c("shift_left", "flexible", "regnorm", "gdpgrow",
          "resgdp", "bopgdp", "useimfcr", "surveil",
          "univers", "resvol", "totvol", "tradedep", 
          "military", "termlim","parli", "lastrest", 
          "lastrest2", "lastrest3")

form <- as.formula(
  paste("restrict ~ art8 +", paste(covs, collapse = " + "))
)

model <- glm(form, data = treaty, family = binomial)

summary(model)

```

This is an observational regression, not a truly randomized experiment. Even with controlling for covariates, there are omitted variable bias. This result reflects association not causal effect.

b\)

```{r}
library(sandwich)
library(lmtest)

cluster_se <- vcovCL(model, cluster = ~ imf_ccode)

coeftest(model, vcov = cluster_se)
```

Clustering should make the evaluation more robust, but no significant change is observed.

c\)

Ridge regression typically shrinks the coefficients towards 0 (with the goal of increasing prediction stability). The goal with this eval is to conduct inference on the art8 coefficient, so utilizing ridge regression is not ideal.
